biological data preperation

### 2018-10-25 src/biological_data_prep.Rmd
obs_by_cell

>>>>

# observations by cell (in total, and also by time step)

as the title says... how many observations happeend in each cell:
- in total
- in each yyyymm

```{r observation by cell - total}
library(plyr) #to use the count function
obs_by_cell <- count(data_aea, "cell_id")
obs_by_cell
write.csv(obs_by_cell, file = "../output/bio/no_observations_cell.csv")
```

```{r}
obs_cell_yymm <- count(data_aea, c("cell_id", "year", "month"))
obs_cell_yymm
write.csv(obs_cell_yymm, file = "../output/bio/no_observations_cell_yymm.csv")
```
